Figures

### 2021-02-22 figure.Rmd
edits: add network panels

```{r, fig.height=6, fig.width=8, fig.cap="(A) Framework for generating theoretical branching river networks. Branching river networks are depicted as a network of connected habitat patches, in which the number of habitat patches $N_p$ and branching probability $P_{b}$ dictate the ecosystem size and complexity ($N_p = 50$ and $P_{b} = \\{0.2, 0.5, 0.8\\}$ in this example). Environmental conditions at headwaters (i.e., the most upstream patches) are drawn randomly from a normal distribution and propagate downstream with local environmental noise (a spatially autoregressive process with white noise; Methods). Habitat patches are colored in proportion to environmental values (similar colors have similar environmental values). In this example, we used values of environmental variation at headwaters $\\sigma_{h} = 1$ and the degree of local environmental noise $\\sigma_{l} = 0.01$. (B) Example of intensively surveyed watersheds in Hokkaido, Japan (the red-colored watershed in C). Red dots indicate sampling sites for fish surveys. (C) Map of study regions (left, Hokkaido, Japan; right, Midwest, US). Watersheds (i.e., metacommunities) are gray-shaded in proportion to the number of sampling sites."}

source(here::here("/empirical/figure_map.R"))

@@

source(here::here("/theory/figure_n_patch.R"))
```

@@

source(here::here("/theory/figure_p_branch.R"))
```

@@

source(here::here("/empirical/figure_diversity.R"))
```

>>>>

```{r, fig.height=6, fig.width=10, fig.cap="(A and B) Theoretical branching networks generated under contrasting landscape scenarios. Branching river networks are depicted as a network of connected habitat patches, in which the number of habitat patches $N_p$ and branching probability $P_{b}$ dictate the ecosystem size and complexity ($N_p = 30$ and $P_{b} = \\{0.2, 0.8\\}$ in this example). Environmental conditions at headwaters (i.e., the most upstream patches) are drawn randomly from a normal distribution and propagate downstream with local environmental noise (Methods). Habitat patches are colored in proportion to environmental values (similar colors have similar environmental values). Panel A and B show distinct landscape scenarios. Environmental variation at headwaters $\\sigma_{h}$ exceeds the degree of local environmental noise $\\sigma_{l}$ in A ($\\sigma_{h} = 1, \\sigma_{l} = 0.01$), while the opposite is true in B ($\\sigma_{h} = 0.01, \\sigma_{l} = 1$). (C) Example of intensively surveyed watersheds in Hokkaido, Japan (the red-colored watershed in D). Red dots indicate sampling sites for fish surveys. (D) Map of study regions (left, Hokkaido, Japan; right, Midwest, US). Watersheds (i.e., metacommunities) are gray-shaded in proportion to the number of sampling sites."}

source(here::here("empirical/figure_map.R"))

@@

source(here::here("theory/figure_n_patch.R"))
```

@@

source(here::here("theory/figure_p_branch.R"))
```

@@

source(here::here("empirical/figure_diversity.R"))
```
